Viral Sequence Sorting Tools Evaluation

### 2022-10-04 EnvironmentalData/DrinkingWaterMetagenomes/identifying_viral_contigs_environmental_dw.Rmd
More dw visualizations.

for (i in c(0,1)){
  for (j in c(0,1)){
    for (k in c(0,1)){
      for (l in c(0,1)){
        for (m in c(0,1)){
          for (n in c(0,1)){
            combos_list$toolcombo[p] <- paste(i,j,k,l,m,n)
            combos_list$CheckV[p] <- i
            combos_list$DVF[p] <- j
            combos_list$Kaiju[p] <- k
            combos_list$VIBRANT[p] <- l
            combos_list$VS[p] <- m
            combos_list$VS2[p] <- n
            p <- p+1
          }
        }
      }
    }
  }
}

@@

  num_viruses$toolcombo[i] <- combos_list$toolcombo[i]
}

num_viruses$numtools <- str_count(num_viruses$toolcombo, "1")
num_viruses <- num_viruses[order(num_viruses$num_viruses, decreasing=F),]
num_viruses$toolcombo <- factor(num_viruses$toolcombo, levels = unique(num_viruses$toolcombo))
num_viruses$numtools <- as.factor(num_viruses$numtools)
```

```{r}
pal <- ggthemes::tableau_color_pal(palette="Tableau 10", type="regular")
ggplot(num_viruses, aes(x=toolcombo, y=num_viruses, 
                                  color=numtools, fill=numtools)) +
  geom_point() +
  theme_light() +
  theme(
    panel.grid.major.y = element_blank(),
    panel.border = element_blank(),
    axis.ticks.y = element_blank(),
    legend.position = "bottom",
    axis.text.y=element_text(size=14),
    axis.text.x=element_text(size=14, angle = 90),
    legend.text=element_text(size=12),
    axis.title=element_text(size=16),
  ) +
  xlab("Tool Combination (CV, DVF, KJ, VB, VS, VS2)") +
  ylab("Num Viruses Predicted")
```

@@

colnames(viral_scores_nozeros) <- num_viruses$toolcombo
```

@@

```{r}
tooldata <- num_viruses
rownames(tooldata) <- tooldata$toolcombo
```

```{r}
physeq_pooled <- phyloseq(otu_table(viral_scores_nozeros, taxa_are_rows = T),
                                     sample_data(tooldata))

ordination <- phyloseq::ordinate(physeq =physeq_pooled, method = "PCoA", distance = "bray")
phyloseq::plot_ordination(physeq = physeq_pooled, ordination = ordination,
                          shape="numtools", color="num_viruses") + 
  geom_point(size = 3) +
  theme_bw() +
  geom_label(label=tooldata$toolcombo)

@@

>>>>

for (i in c(0,1)){
  for (j in c(0,1)){
    for (k in c(0,1)){
      for (l in c(0,1)){
        for (m in c(0,1)){
          for (n in c(0,1)){
            combos_list$toolcombo[p] <- paste(i,j,k,l,m,n)
            combos_list$toolcombo2[p] <- paste(if(i){"C"}else{"0"},if(j){"DVF"}else{"0"},
                                               if(k){"K"}else{"0"},if(l){"VB"}else{"0"},
                                               if(m){"VS"}else{"0"},if(n){"VS2"}else{"0"})
            combos_list$CheckV[p] <- i
            combos_list$DVF[p] <- j
            combos_list$Kaiju[p] <- k
            combos_list$VIBRANT[p] <- l
            combos_list$VS[p] <- m
            combos_list$VS2[p] <- n
            p <- p+1
          }
        }
      }
    }
  }
}

@@

  num_viruses$toolcombo[i] <- combos_list$toolcombo[i]

  num_viruses$toolcombo2[i] <- combos_list$toolcombo2[i]
}

num_viruses$numtools <- str_count(num_viruses$toolcombo, "1")
num_viruses <- num_viruses[order(num_viruses$num_viruses, decreasing=F),]
num_viruses$toolcombo <- factor(num_viruses$toolcombo, levels = unique(num_viruses$toolcombo))
num_viruses$toolcombo2 <- factor(num_viruses$toolcombo2, levels = unique(num_viruses$toolcombo2))
num_viruses$numtools <- as.factor(num_viruses$numtools)
```

```{r}
ggplot(num_viruses, aes(x=toolcombo, y=num_viruses, 
                                  color=numtools, fill=numtools)) +
  geom_point() +
  theme_light() +
  theme(
    panel.grid.major.y = element_blank(),
    panel.border = element_blank(),
    axis.ticks.y = element_blank(),
    legend.position = "bottom",
    axis.text.y=element_text(size=14),
    axis.text.x=element_text(size=14, angle = 90),
    legend.text=element_text(size=12),
    axis.title=element_text(size=16),
  ) +
  xlab("Tool Combination (CV, DVF, KJ, VB, VS, VS2)") +
  ylab("Num Viruses Predicted")

ggplot(num_viruses, aes(x=toolcombo2, y=num_viruses, 
                                  color=numtools, fill=numtools)) +
  geom_point() +
  theme_light() +
  theme(
    panel.grid.major.y = element_blank(),
    panel.border = element_blank(),
    axis.ticks.y = element_blank(),
    legend.position = "bottom",
    axis.text.y=element_text(size=14),
    axis.text.x=element_text(size=14, angle = 90),
    legend.text=element_text(size=12),
    axis.title=element_text(size=16),
  ) +
  xlab("Tool Combination (CV, DVF, KJ, VB, VS, VS2)") +
  ylab("Num Viruses Predicted")
```

@@

colnames(viral_scores_nozeros) <- num_viruses$toolcombo2
```

@@

```{r}
tooldata <- num_viruses

rownames(tooldata) <- tooldata$toolcombo2
```

```{r}
physeq_pooled <- phyloseq(otu_table(viral_scores_nozeros, taxa_are_rows = T),
                                     sample_data(tooldata))
```

```{r}
ordination <- phyloseq::ordinate(physeq =physeq_pooled, method = "PCoA", distance = "bray")
phyloseq::plot_ordination(physeq = physeq_pooled, ordination = ordination,
                          shape="numtools", color="num_viruses") + 
  geom_point(size = 3) +
  theme_bw() +
  geom_label(label=tooldata$toolcombo)

@@

```{r}
bray_dist <- phyloseq::distance(physeq_pooled, method="bray")
clusters <- hclust(dist(bray_dist))
plot(clusters)

myclusters <- cutree(clusters, h=0.8)
```

```{r}
names(myclusters[myclusters==1])
names(myclusters[myclusters==2])
names(myclusters[myclusters==3])
names(myclusters[myclusters==4])
names(myclusters[myclusters==5])
